Hybrid platforms and bargaining

### 2023-06-11 src/presentation/io_day.qmd
Add crossrefs

## Profit sharing

::: {.fragment}
 - Players get their Shapley-values 
   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
:::
::: {.fragment}
 - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1f(N_P, sN_F) \mathrm{d}s $$
 - Fringe gets the rest
:::
::: {.fragment}
 - Can be extended with weighting (innate bargaining power)
:::

@@

## Demand

@@

::: {.incremental}
 - Optimal entry fee is independent of $N_P$:
   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
 - Size of the aggregate is independent* of $N_P$:
   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
 - **Consumer surplus** is also **independent*** of $N_P$:
   $$ CS^* \propto \log(A^*) $$
:::

@@

## The Shapley-value

@@

@@

## Value of the platform

@@

::: {.fragment .fade-in fragment-index=2}
Shapley value:
$$l 
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
:::
::: {.fragment .fade-in fragment-index=5}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

>>>>

## Profit sharing {#sec-profit-sharing}

::: {.fragment}
 - Players get their Shapley-values 
   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
:::
::: {.fragment}
 - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1f(N_P, sN_F) \mathrm{d}s $$
 - Fringe gets the rest
:::

::: {.crossref}
Shapley-value: @sec-shapley-value

Value of the platform: @sec-platform-value
:::

@@

## Demand {#sec-demand}

@@

::: {.incremental}
 - Optimal entry fee is independent of $N_P$:
 - Size of the aggregate is independent* of $N_P$:
   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
 - **Consumer surplus** is also **independent*** of $N_P$:
   $$ CS^* \propto \log(A^*) $$
:::

@@

## The Shapley-value {#sec-shapley-value}

@@

::: {.crossref}
Back: @sec-profit-sharing
:::

@@

## Value of the platform {#sec-platform-value}

@@

::: {.fragment .fade-in fragment-index=2}
Shapley value:
$$
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
:::
::: {.fragment .fade-in fragment-index=5}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

::: {.crossref}
Back: @sec-profit-sharing
:::

@@

::: {.crossref}
Back: @sec-demand
:::
